Supporting Information: Improving cropland maps through tight integration of human and machine intelligence

### 2020-07-30 inst/manuscript/figures.Rmd
Added figures and results from image quality assessment. Added function that uses row, col information from probability information to get x y from reference grid.

p1 <- ggplot() + 
  geom_sf(data = africa, fill = "gray90", color = "grey50", size = 0.2) +
  geom_sf(data = ghana, fill = "grey85", col = "transparent", size = 0.3) +
  geom_sf(data = degrees %>% filter(grid %in% ghana_degrees),
          fill = "transparent", col = "grey70", size = 0.4, lty = 3) +
  geom_sf(data = aois, fill = "transparent", col = "black", size = 0.4) +
  geom_sf(data = aois %>% filter(aois == ind), col = "black", fill = "gray70", 
          size = 0.4) +
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) +
  theme_void()

@@

## Results 
### Figure 4: Composite quality
```{r, eval=FALSE, fig.cap="Placeholder for composite quality image."}
data("image_quality")
tile_quality <- image_quality %>% filter(worker_id == 98) %>% 
  group_by(name, season) %>% 
  summarize(tile = min(tile), Score = sum(score) / 12) %>% ungroup() %>% 
  inner_join(tiles, .)

# nms <- image_quality %>% group_by(name, worker_id) %>% count() %>% ungroup() %>% 
#   filter(worker_id == 98) %>% pull(name)
# image_quality %>% filter(worker_id != 98 & !name %in% nms)
# image_quality %>% filter(name, worker_id)
xylims <- st_coordinates(ghana)
maprange <-  c(range(xylims[, 1]), range(xylims[, 2]))
pal <- colorRampPalette(rev(brewer.pal(9, "RdBu")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(1, 8))

p1 <- ggplot(africa) + geom_sf(fill = "gray97", color = "grey", size = 0.25) +
  geom_sf(data = tiles, fill = "grey85", col = "grey", size = 0.3) +
  geom_sf(data = ghana, fill = "transparent", col = "grey", size = 0.3) +
  geom_sf(data = tile_quality, mapping = aes(fill = Score, color = Score)) +  
  scale_fill_gradientn(colours = pal(20)) + 
  scale_color_gradientn(colours = pal(20)) + 
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) + 
  theme_void()
p1
```

@@

# plot
p <- ggplot(imetrics) + 
  geom_line(aes(Iteration, Score, color = AOI, size = AOI)) +
  geom_point(data =  mx_metrics, aes(Iteration, Score, color = AOI), 
             size = 1) +
  ggrepel::geom_text_repel(
    data = mx_metrics %>% filter(AOI != "All"), 
    aes(label = AOI, x = Iteration, y = Score), col = "grey50", 
    segment.color = "grey80", point.padding = 0.05 
  ) +
  scale_color_manual(values = cols, guide = FALSE) +
  scale_size_manual(values = lsize, guide = FALSE) + 
  scale_y_continuous(breaks = seq(0.2, 1, 0.1), expand = c(0, 0), 
                     limits = c(0.2, 1)) + 
  facet_wrap(vars(Metric), ncol = 3) + 
  theme_linedraw() + 
  theme(strip.background = element_rect(fill = "white"))+
  theme(strip.text = element_text(colour = "black"))

>>>>

p1 <- ggplot() + 
  geom_sf(data = africa, fill = "gray90", color = "grey50", size = 0.2) +
  geom_sf(data = ghana, fill = "grey85", col = "transparent", size = 0.3) +
  geom_sf(data = degrees %>% filter(grid %in% ghana_degrees),
          fill = "transparent", col = "grey70", size = 0.4, lty = 3) +
  geom_sf(data = aois, fill = "transparent", col = "black", size = 0.4) +
  geom_sf(data = aois %>% filter(aois == ind), col = "black", fill = "gray70", 
          size = 0.4) +
  geom_sf_text(data = aois, aes(label = aois)) + 
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) +
  theme_void()

@@

## Results 
### Figure 4: Composite quality
```{r, eval=FALSE}
data("image_quality")

# plot parameters
xylims <- st_coordinates(ghana)
maprange <-  c(range(xylims[, 1]), range(xylims[, 2]))
pal <- colorRampPalette(rev(brewer.pal(9, "RdBu")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(1, 8))

leglabs <- seq(0.4, 1, 0.1)
p1 <- ggplot(africa) + geom_sf(fill = "gray97", color = "grey", size = 0.25) +
  geom_sf(data = tiles, fill = "grey85", col = "grey", size = 0.3) +
  geom_sf(data = ghana, fill = "transparent", col = "grey", size = 0.3) +
  geom_sf(data = image_quality$tile, 
          mapping = aes(fill = Score, color = Score)) +
  facet_wrap(vars(season), ncol = 2) +
  scale_fill_gradientn(colors = pal(7), 
                       breaks = seq(0.4, 1, 0.1), limits = c(0.4, 1),
                       labels = leglabs) + 
  scale_color_gradientn(colors = pal(7), 
                        breaks = seq(0.4, 1, 0.1), limits = c(0.4, 1), 
                        labels = leglabs) + 
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) + 
  theme_linedraw() + 
  theme(legend.position="bottom", 
        strip.background = element_rect(fill = "white"), 
        strip.text = element_text(colour = "black"), 
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())

p2 <- ggplot(as_tibble(image_quality$tile)) +
  geom_histogram(aes(x = Score), fill = "blue", col = "grey", #bins = 10, 
                 binwidth = 0.05, boundary = 0.1) + 
  scale_x_continuous(breaks = leglabs, labels = leglabs, expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 30)) +
  facet_wrap(vars(season), ncol = 2) + 
  ylab("Count") + 
  theme_linedraw() + 
  theme(strip.background = element_rect(fill = "white"), 
        strip.text = element_text(colour = "black"))

g <- cowplot::plot_grid(p1, p2, nrow = 2, align = "hv", axis = "l",
                        labels = LETTERS[1:2], label_x = 0, 
                        label_y = c(0.97, 1),   
                        scale = c(1, 1), rel_heights = c(1, 0.7))
ggsave(pth("figures/figure4.png"), 
       width = 4, height = 6.5, units = "in", dpi = 300)

@@

# plot
p <- ggplot(imetrics) + 
  geom_line(aes(Iteration, Score, color = AOI, size = AOI)) +
  geom_point(data =  mx_metrics, aes(Iteration, Score, color = AOI), 
             size = 1) +
  ggrepel::geom_text_repel(
    data = mx_metrics %>% filter(AOI != "All"), 
    aes(label = AOI, x = Iteration, y = Score), col = "grey50", 
    segment.color = "grey80", point.padding = 0.05 
  ) +
  scale_color_manual(values = cols, guide = FALSE) +
  scale_size_manual(values = lsize, guide = FALSE) + 
  scale_y_continuous(breaks = seq(0.2, 1, 0.1), expand = c(0, 0), 
                     limits = c(0.2, 1)) + 
  facet_wrap(vars(Metric), ncol = 3) + 
  theme_linedraw() + 
  theme(strip.background = element_rect(fill = "white"), 
        theme(strip.text = element_text(colour = "black"))

### 2020-07-30 inst/manuscript/manuscript.Rmd
Added figures and results from image quality assessment. Added function that uses row, col information from probability information to get x y from reference grid.

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: yes
    template: manuscript.latex
    includes:
      in_header: header.tex

@@

```{r, echo = FALSE, out.width="50%", fig.cap="An overview of the primary system components, the data stores that hold the inputs and outputs from each component, and the direction of connections between them. The dashed line indicates iterative interactions, while solid lines indicate one-time or irregular connections.", fig.align='center'}
knitr::include_graphics('figures/figure1.png')
```

@@

```{r, echo = FALSE, out.width="100%", fig.cap="An overview of analytical scales used in the mapping platform, including A) the areas of interest defining the minimum mapping geography (solid black lines; dotted lines indicate boundaries of 1 degree grid), the B) 0.05 degree grid used for creating image composite tiles, and the C) 0.005 degree resolution reference grid used for collecting training data and distributed computing.", fig.align='center'}
knitr::include_graphics('figures/figure2.png')
```
The temporal compositing process is applied to the ARD imagery for the time period of interest, which in the case of this study is one of two multi-month seasons, the primary growing and dry seasons for a single agricultural year. Imagery from two seasons helps to improve the performance of cropland classifiers [@Debatsgeneralizedcomputervision2016], while having the seasons in same year helps to minimize differences caused by land change. For each pixel in each image in each ARD temporal stack for a given season, we calculate two weights, with the first being:

@@

After fitting, the model is applied to the features of the model validation set, and a set of accuracy metrics are calculated, including ordinary binary accuracy and the true skill statistic [@AlloucheAssessingaccuracyspecies2006], which is considered to be more effective than the Kappa statistic in that it controls for class prevalence.

@@

@@

## Image catalog
We generated a complete image catalog for the `r nrow(tiles)` tiles intersecting Ghana, spanning `r km2` km$^2$. This entailed processing all PlanetScope imagery intersecting the total extent of these tiles for the periods May-September, 2018 (the growing season) and December, 2018 to February, 2019 (the subsequent dry season). The longer period was necessary for the growing season because of the high frequency of cloud cover, which severely limits the number of clear scenes over any given area. For cloudier regions (AOIs 10, 11, 13, 14, 16) we started the dry season window in November. The compositing processes was applied to render the resulting seasonally contrasting image pairs for each tile (**Figure Xa**). We also collected and composited imagery for one of the 16 AOIs for the two seasons of the 2019 agricultural year. All images were converted into Raster Foundry slippy maps for presentation in *labeller*.

We evaluated the overall quality of the resulting composites across the region using a random selection of 100 tiles, which we graded according to a four category quality score that evaluated the degree of residual 1) cloud and 2) cloud shadow, 3) the number of visible scene boundary artifacts, and 4) the proportion of the image in which resolution was degraded below the 3-4 m PlanetScope resolution, due to between-date image mis-registrations. Each category was qualitatively ranked from 0-3, with 0 being the lowest quality, and 3 the highest (see SI for complete protocol), thus the highest possible score was 12. The results showed that the majority of the sampled composites (**X%; Fig Xb**) received a score of **X** or higher (**Y and Z%**), as rated by four independent observers (mean standard deviation of observer scores was **XX**). Image quality varied spatially and temporally, with the lower quality images found during in the growing season period and the Southwest corner, where the substantially greater cloud cover resulting in a much lower density of available PlanetScope imagery for each time period (**Fig Xc**). Overall, the available image density and quality of composites were closely related (see SI for full details).

```{r, echo = FALSE, out.width="70%", fig.cap="The location and quality scores of 100 randomly selected tiles for the growing (A) and off-growing season (B), and the corresponding distributions of the quality scores for each season, respectively (C and D) [This a hypothetical placeholder figure].", fig.align='center'}
knitr::include_graphics('figures/figure4.png')
```

@@

### Model performance
The gain in model performance was assessed for each AOI and for each iteration using a variety of metrics, including overall accuracy, area under the curve of the Receiver Operating Characteristic (AUC), and the F1 score (Figure \ref{fig:alperformance}).

@@

The average performance associated

**[Fill in with intro]**. The average number of iterations per active learning process was **4**, as overall performance gains, as assessed against validation sets, saturated quickly (see **Figure X** in SI).

The average computational time per iteration per AOI was *6 hours*. **Training time. Interaction time**

>>>>

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: yes
    extra_dependencies: ["flafter"]
    template: manuscript.latex
    includes:
      in_header: header.tex

@@

```{r aois, echo = FALSE, out.width="50%", fig.cap="An overview of the primary system components, the data stores that hold the inputs and outputs from each component, and the direction of connections between them. The dashed line indicates iterative interactions, while solid lines indicate one-time or irregular connections.", fig.align='center'}
knitr::include_graphics('figures/figure1.png')
```

@@

```{r, echo = FALSE, out.width="100%", fig.cap="The reference system used in the mapping platform, including A) numbered areas of interest (AOIs) that define the minimum mapping geography (solid black lines; dotted lines indicate boundaries of 1 degree grid), B) the 0.05 degree tile used for compositing imagery, and C) the 0.005 degree resolution reference grid used for collecting training data and distributed computing.", fig.align='center'}
knitr::include_graphics('figures/figure2.png')
```
The temporal compositing process is applied to the ARD imagery for the time period of interest, which in the case of this study is one of two multi-month seasons, the primary growing and dry seasons for a single agricultural year. Imagery from two seasons helps to improve the performance of cropland classifiers [@Debatsgeneralizedcomputervision2016], while having the seasons in same year helps to minimize differences caused by land change. For each pixel in each image in each ARD temporal stack for a given season, we calculate two weights, with the first being:

@@

After fitting, the model is applied to the features of the model validation set, and a set of accuracy metrics are calculated, including ordinary binary accuracy, the F1 score, and the area under the curve of the Receiver Operating Characteristic [@Pontiustotaloperatingcharacteristic2014].

@@

### Image quality assessment
```{r, echo=FALSE}
data("image_quality")
tile_quality <- image_quality %>% filter(kml_type == "F") %>% 
  group_by(name, season, worker_id) %>% 
  summarize(tile = min(tile), Score = sum(score) / 12) %>% ungroup() 
tilen <- tile_quality %>% distinct(tile) %>% count() %>% pull(n)
```

We evaluated the overall quality of the resulting seasonal image composites across the region using a random selection of `r tilen`, which we graded according to a four category quality score that evaluated the degree of residual 1) cloud and 2) cloud shadow, 3) the number of visible scene boundary artifacts, and 4) the proportion of the image in which resolution was degraded below the 3-4 m PlanetScope resolution (e.g. because of between-date image mis-registrations). Each category was qualitatively ranked from 0-3, with 0 being the lowest quality, and 3 the highest (see SI for complete protocol), making the highest possible score 12. We rescaled scores to fall between 0 and 1.

@@

## Image catalog
```{r, echo=FALSE}
tqual_mu <- image_quality$tile %>%
  group_by(season, tile) %>% 
  summarize(score = mean(Score)) %>% 
  ungroup()
tqual_sum <- tqual_mu %>% 
  group_by(season) %>% 
  summarize(mu = mean(score), sd = sd(score))
tqmu <- tqual_sum %>% pull(mu) %>% round(2)
names(tqmu) <- tqual_sum %>% pull(season)

tqual_ct <- tqual_mu %>% group_by(season) %>% 
  mutate(gt85 = ifelse(score > 0.85, 1, 0)) %>% 
  summarize(n = n(), n85 = sum(gt85)) %>% 
  mutate(prop = n85 / n)
tqct <- tqual_ct %>% pull(prop) * 100
names(tqct) <- tqual_ct %>% pull(season)
```

We generated a complete image catalog for the `r nrow(tiles)` tiles intersecting Ghana, spanning `r km2` km$^2$. This entailed processing all PlanetScope imagery intersecting the total extent of these tiles for the periods May-September, 2018 (the growing season) and December, 2018 to February, 2019 (the subsequent dry season). The longer period was necessary for the growing season because of the high frequency of cloud cover, which severely limits the number of clear scenes over any given area. For cloudier regions (AOIs 10, 11, 13, 14, 16) we started the dry season window in November. The compositing processes was applied to render the resulting seasonally contrasting image pairs for each tile. We also composited imagery for AOI 8 (Figure \ref{fig:aois}A) for the two seasons of the 2019 agricultural year. All images were converted into Raster Foundry slippy maps for presentation in *labeller*.

An assessment with two observers (see SI for observer details) found that average quality per growing season composite tile was `r tqmu["gs"]`, with `r tqct["gs"]` percent having scores $\geq$ 0.85, while the average quality of dry season composites was `r tqmu["os"]` (`r tqct["os"]` percent $\geq$ 0.85). Composite quality in both seasons was highest in the northern half of the country and lowest in the southwest (Figure \ref{fig:imqual}A), where the substantially greater cloud cover resulted in a much lower density of available PlanetScope imagery for each time period.

<!-- Overall, the available image density and quality of composites were closely related (see SI for full details).   -->

```{r imqual, echo = FALSE, out.width="70%", fig.cap="The location and quality scores of 100 randomly selected tiles for the growing (A) and off-growing season (B), and the corresponding distributions of the quality scores for each season, respectively (C and D) [This a hypothetical placeholder figure].", fig.align='center'}
knitr::include_graphics('figures/figure4.png')
```

@@

### Model performance
```{r, echo=FALSE}
data("iteration_metrics")
delta_func <- function(x, rnd = 4) round((x - lag(x)) / lag(x), rnd)

# Difference iteration 0 to 3
imet_mu03 <- iteration_metrics %>% 
  filter(AOI == "All") %>%
  filter(Iteration %in% c(0, 3)) %>%
  filter(!grepl("_change", Metric)) %>% 
  group_by(Metric) %>% 
  mutate(dscore = delta_func(Score)) %>% 
  ungroup() %>% 
  mutate(dscore = round(dscore * 100, 1))

imet_mu0 <- imet_mu03 %>% filter(Iteration == 0) %>% 
  mutate(Score = round(Score, 3))
imet_mu3 <- imet_mu03 %>% filter(Iteration == 3) %>% 
  mutate(Score = round(Score, 3))

# differences per iteration
imet_dmu <- iteration_metrics %>% 
  filter(AOI == "All" & Iteration > 0) %>%
  filter(grepl("_change", Metric)) %>% 
  mutate(Metric = gsub("_change", "", Metric)) %>% 
  mutate(Score = round(Score * 100, 1)) %>% 
  filter(Metric %in% c("Accuracy", "AUC", "F1"))

imet_dmu1 <- imet_dmu %>% filter(Iteration == 1) %>% 
  mutate(dscore = round(Score, 3))
imet_dmu2 <- imet_dmu %>% filter(Iteration == 2) %>% 
  mutate(dscore = round(Score, 3))
imet_dmu3 <- imet_dmu %>% filter(Iteration == 3) %>% 
  mutate(dscore = round(Score, 3))

# AOI score ranges
imet_min <- iteration_metrics %>% group_by(AOI) %>%
  filter(Iteration == max(Iteration) & !grepl("change", Metric)) %>%
  filter(Metric %in% c("Accuracy", "AUC", "F1")) %>% 
  ungroup() %>% 
  group_by(Metric) %>% 
  filter(Score == min(Score)) %>% 
  mutate(AOI = gsub("labeller", "", AOI), Score = round(Score, 3))

imet_max <- iteration_metrics %>% group_by(AOI) %>%
  filter(Iteration == max(Iteration) & !grepl("change", Metric)) %>%
  filter(Metric %in% c("Accuracy", "AUC", "F1")) %>% 
  ungroup() %>% 
  group_by(Metric) %>% 
  filter(Score == max(Score)) %>% 
  mutate(AOI = gsub("labeller", "", AOI), Score = round(Score, 3))
```

The gain in model performance was assessed for each AOI against several accuracy metrics. The average accuracy, AUC, and F1 at Iteration 0 were `r imet_mu0 %>% filter(Metric == "Accuracy") %>% pull(Score)`, `r imet_mu0 %>% filter(Metric == "AUC") %>% pull(Score)`, and `r imet_mu0 %>% filter(Metric == "F1") %>% pull(Score)`, respectively, increasing to `r imet_mu3 %>% filter(Metric == "Accuracy") %>% pull(Score)`, `r imet_mu3 %>% filter(Metric == "AUC") %>% pull(Score)`, and `r imet_mu3 %>% filter(Metric == "F1") %>% pull(Score)` by Iteration 3 (Figure \ref{fig:alperformance}). These differences represent respective gains of `r imet_mu3 %>% filter(Metric == "Accuracy") %>% pull(dscore)`, `r imet_mu3 %>% filter(Metric == "AUC") %>% pull(dscore)`, and
`r imet_mu3 %>% filter(Metric == "F1") %>% pull(dscore)` for the three metrics. The largest gains in each metric were registered on Iteration 1, averaging `r imet_dmu1 %>% filter(Metric == "Accuracy") %>% pull(Score)`, `r imet_dmu1 %>% filter(Metric == "AUC") %>% pull(Score)`, and `r imet_dmu1 %>% filter(Metric == "F1") %>% pull(Score)` percent for accuracy, AUC, and F1. The lowest gains were received on Iteration 3 for accuracy (`r imet_dmu3 %>% filter(Metric == "Accuracy") %>% pull(Score)`%) and F1 (`r imet_dmu3 %>% filter(Metric == "F1") %>% pull(Score)`%), while Iteration 2 showed the lowest average gain for AUC (`r imet_dmu3 %>% filter(Metric == "AUC") %>% pull(Score)`%). The range in scores varied substantially across AOIs and metrics. Accuracy ranged between `r imet_min %>% filter(Metric == "Accuracy") %>% pull(Score)` (AOI `r imet_min %>% filter(Metric == "Accuracy") %>% pull(AOI)`) and `r imet_max %>% filter(Metric == "Accuracy") %>% pull(Score)` (AOI `r imet_max %>% filter(Metric == "Accuracy") %>% pull(AOI)`), while AUC varied from `r imet_min %>% filter(Metric == "AUC") %>% pull(Score)` (AOI `r imet_min %>% filter(Metric == "AUC") %>% pull(AOI)`) and `r imet_max %>% filter(Metric == "AUC") %>% pull(Score)` (AOI `r imet_max %>% filter(Metric == "AUC") %>% pull(AOI)`), and F1 from `r imet_min %>% filter(Metric == "F1") %>% pull(Score)` (AOI `r imet_min %>% filter(Metric == "F1") %>% pull(AOI)`) and `r imet_max %>% filter(Metric == "F1") %>% pull(Score)` (AOI `r imet_max %>% filter(Metric == "F1") %>% pull(AOI)`).

@@

### 2020-07-30 inst/manuscript/si.Rmd
Added figures and results from image quality assessment. Added function that uses row, col information from probability information to get x y from reference grid.

# Methods
## Assessing quality of composites
The rubric presented in Table 1 was used to assess the quality of the seasonal image composites. The imagery was evaluated by examining their Raster Foundry overlays within a `labeller` instance set up for the purpose.

```{r, echo=FALSE, message=FALSE}
library(kableExtra)
image_qual_criteria <- tibble(
  `Quality dimension` = c(
    "Percent affected by residual cloud", "Percent affected by cloud shadow", 
    "Number of visible scene boundaries", "Percent blurred"
  ),
  `3 pts` = c("<1%", "<1%", "None", "None"), 
  `2 pts` = c("1-5%", "1-5%", "1", "<20%"), 
  `1 pts` = c("5-10%", "5-10%", "2-3", "20-50%"),
  `0 pts` = c(">10%", ">10%", ">3", ">50%")
) 
cap <- glue::glue("Four dimensions used to assess the assess the quality
                  of the temporally composited image tiles, including the
                  criteria used to award points for scoring each dimension.")
kable(image_qual_criteria, format = "latex", booktabs = "T", caption = cap) %>% 
  kable_styling(full_width = TRUE, latex_options = c("hold_position")) %>% 
  column_spec(1, width = "8cm")
```

@@

#### Response design
##### Stage 1
We collected the map reference sample on a separate instance of `labeller` set up for the purpose (`validator.crowdmapper.org`). For the sampling unit, we selected a rectangular polygon of ~0.1 ha (0.0002866$^\circ$ resolution), centered on the centroid of each grid cell selected for map reference sample.  Four classes were established for the validation: **cropland**, **non-cropland**, **uncertain but likely cropland**, and **uncertain but likely non-cropland**. The latter two classes were designed to capture information related to swidden dynamics, following the rationale that uncertainty and time since last cropping are likely to be positively correlated. This uncertainty also captures information about the inherent difficulty of the mapping task. Samples were collected by visually interpreting the overlays of PlanetScope composites presented in `labeller`, following the same interpretation protocols used by the labelling team, with the exception that the polygons placed were square and of 0.0002866$^\circ$ resolution.

@@

\clearpage
# Results
## Image quality

>>>>

# Methods
## Assessing quality of composites
The rubric presented in Table \ref{tab:imqcriteria} was used to assess the quality of the seasonal image composites. The imagery was evaluated by examining their Raster Foundry overlays within a `labeller` instance set up for the purpose.

```{r imqcriteria, echo=FALSE, message=FALSE}
library(kableExtra)
image_qual_criteria <- tibble(
  `Quality dimension` = c(
    "Percent affected by residual cloud", "Percent affected by cloud shadow", 
    "Number of visible scene boundaries", "Percent blurred"
  ),
  `3 pts` = c("<1%", "<1%", "None", "None"), 
  `2 pts` = c("1-5%", "1-5%", "1", "<20%"), 
  `1 pts` = c("5-10%", "5-10%", "2-3", "20-50%"),
  `0 pts` = c(">10%", ">10%", ">3", ">50%")
) 
cap <- glue::glue("Four dimensions used to assess the assess the quality
                  of the temporally composited image tiles, including the
                  criteria used to award points for scoring each dimension.")
kable(image_qual_criteria, format = "latex", booktabs = "T", caption = cap) %>% 
  kable_styling(full_width = TRUE, latex_options = c("hold_position")) %>% 
  column_spec(1, width = "8cm")
```

@@

#### Response design

##### Stage 1
We collected the map reference sample on a separate instance of `labeller` set up for the purpose (`validator.crowdmapper.org`). For the sampling unit, we selected a rectangular polygon of ~0.1 ha (0.0002866$^\circ$ resolution), centered on the centroid of each grid cell selected for map reference sample.  Four classes were established for the validation: **cropland**, **non-cropland**, **uncertain but likely cropland**, and **uncertain but likely non-cropland**. The latter two classes were designed to capture information related to swidden dynamics, following the rationale that uncertainty and time since last cropping are likely to be positively correlated. This uncertainty also captures information about the inherent difficulty of the mapping task. Samples were collected by visually interpreting the overlays of PlanetScope composites presented in `labeller`, following the same interpretation protocols used by the labelling team, with the exception that the polygons placed were square and of 0.0002866$^\circ$ resolution.

@@

\clearpage
# Results
## Image quality
```{r, echo=FALSE}
data("image_quality")
wqual_diff <- image_quality$img %>% filter(kml_type == "F") %>%
  group_by(name, season, worker_id) %>%
  summarize(tile = min(tile), score = sum(score) / 12) %>% 
  ungroup() %>% 
  pivot_wider(names_from = worker_id, values_from = score,
              names_prefix = "w") %>%
  select(tile, season, w92, w99) %>% 
  mutate(d = w92 - w99, 
         absd = abs(d))
```

The image quality assessment was conducted by two separate observers (L. Song and Q. Zhang). Each observer assessed the composites for each season at all 50 of the randomly selected tiles (see main text) following the defined criteria (Table \ref{tab:imqcriteria}). To calculate the score for a given tile for each season, we summed the ranking across the four categories for each observer, rescaled the values, and then calculated the mean tile score across both observers by season. The mean difference between the two observers was `r d <- round(mean(wqual_diff$d), 3); d` (sd = `r absd <- round(sd(wqual_diff$d), 3); absd`) and the mean absolute difference was `r round(mean(wqual_diff$absd), 3)` (sd = `r round(sd(wqual_diff$absd), 3)`), thus one observer scored tiles about `r abs(round(d * 100))` percent lower than the other observer, on average.
